### 2021-09-02 sections/appendix/descrete_event_simulation/main.tex
Write more documentation around the code

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable. 
% TODO Add more documentation (instructions on how to use code)

>>>>

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable.

This discrete event simulation model was built in python and can be installed by 
running the following command in the terminal:
\begin{lstlisting}[language=bash, style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

Having installed the package, the following script can be used to simulate, and 
get all required performance measures, of a queueing system with two waiting 
spaces and two types of individuals for a runtime of 2000 unit time with the 
following parameters:

\begin{multicols}{2}
    \begin{itemize}
        \centering
        \item \( \lambda_1 = 2 \)
        \item \( \lambda_2 = 3 \)
        \item \( \mu = 1 \)
        \item \( C = 6 \)
        \columnbreak
        \item \( T = 10 \)
        \item \( N = 20 \)
        \item \( M = 10 \)
        \item \( R = 1 \)
    \end{itemize}
\end{multicols}

\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}

The script above shows the outcome of the DES model for a single run.
To minimise the stochasticity of the simulation, the model can be simulated for 
numerous trials. 
The following script can be used to run the simulation for a number of times 
and get the mean of the waiting, service and blocking times:

\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}

Finally, the proportion of individuals within target for multiple runs can be
calculated by running the following block of code:

\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}
